\texttt{MSnbase}, efficient and elegant R-based processing and visualisation of raw mass spectrometry data

### 2020-06-24 msnbase2.Rnw
fix: remove duplicated some
Amend according to @sgibb's suggestion

\color{red}{Because the on-disk backend does not hold all the data in memory,
  direct data manipulations are not possible. We thus implemented a \textit{lazy
  processing} mechanism in this backend that caches any data manipulation
operations on m/z and intensity values}
\sout{The on-disk backend also offers efficient data manipulation by way of
\textit{lazy processing} in the object itself. Operations on the \sout{raw}\color{red}{MS}
data are stored} in a processing queue and only effectively
\sout{applied}\color{red}{applies them}
when the user accesses m/z or intensity values. \color{red}{As an additional
  advantage, operations on subsets of the data become much faster since data
  manipulations are applied only to data subsets instead of the full data set
  at once. Also, data access in on-disk backends is parallelized by data file
  ensuring a higher performance of this backend over conventional in-memory data
  representations.} 
As an example, the
following short analysis pipeline, that can equally be applied to
in-memory or on-disk data, retains MS2 spectra acquired between 1000
and 3000 seconds, extracts the m/z range corresponding to the TMT
6-plex range and focuses on the MS2 spectra with a precursor intensity
greater than $11 \times 10^6$ (the median precursor intensity).

>>>>

\color{red}{Because the on-disk backend does not hold all the data in memory,
  direct data manipulations are not possible. We thus implemented a \textit{lazy
  processing} mechanism in this backend that caches any data manipulation
operation in a processing queue in the object itself. Only when the user
accesses m/z or intensity values these operations are applied}.
\sout{The on-disk backend also offers efficient data manipulation by way of
\textit{lazy processing} in the object itself. Operations on the raw
data are stored in a processing queue and only effectively applied
when the user accesses m/z or intensity values. \color{red}{As an additional
  advantage, operations on subsets of the data become much faster since data
  manipulations are applied only to data subsets instead of the full data set
  at once. Also, data access in on-disk backends is parallelized by data file
  ensuring a higher performance of this backend over conventional in-memory data
  representations.} 
As an example, the
following short analysis pipeline, that can equally be applied to
in-memory or on-disk data, retains MS2 spectra acquired between 1000
and 3000 seconds, extracts the m/z range corresponding to the TMT
6-plex range and focuses on the MS2 spectra with a precursor intensity
greater than $11 \times 10^6$ (the median precursor intensity).
